Staged Abstract Interpreter

### 2018-01-27 paper/paper.tex
update structure and references

\textbf{Outline(Proposed)}.

1. Revisit abstract compilation (generates textual program and closures)

2. Generalize the idea to staged abstract interpreter.
We implement staged abstract interpreter within a big-step abstract semantics 
(abstract definitional interpreter) using Scala with LMS framework.
(ADI in Racket: \url{https://github.com/plum-umd/ abstracting-definitional-interpreters/}).
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

3. Improve performance (closure is still not an efficient enough representation).

Show it generates sound and high-performance low-level analysis code with 
various precisions and sensitivities, for instances, k-CFA, pushdown or m-CFA.

@@

4. Modular analysis for free?

@@

5. Show the evaluation result on benchmark programs. 
Compare with normal abstract interpreter, 
abstract compilation\cite{Boucher:1996:ACN:647473.727587}, and OAAM \cite{Johnson:2013:OAA:2500365.2500604}.
Benchmarks and other reference implementations: \url{https://github.com/ilyasergey/reachability}.

6. Discussion

Big-step vs small-step

@@

\section{Background}

\subsection{Abstracting Abstract Machine}

\subsection{Staged Interpreter}

>>>>

\cite{Boucher:1996:ACN:647473.727587}'s work is esentially a partial evaluated
CE abstract interpreter written in a big-step semantics for CPS. The analysis
it can perform is monovariant. We reproduce their abstractly complied analysis
by adding explicit staging annotation to CE abstract interpreter.
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

\subsection{CPS Syntax and Concrete Interpreter}

\subsection{Abstract Semantics}

\subsection{Staged Abstract CE Interpreter}

Generalize the idea to staged CESK abstract machine for direct style (or ANF), 
which has fully power for instantiating different analyses.

Olivier Danvy shows the relation between small-step CEK machine and big-step
CEK machine by applying a lightweight fix-point promotion. And it is well-known
that a staged interpreter (big-step abstract machine) is a compiler. 
Then a nature question is to ask what is the relation of their abstract 
counterparts.

We may show: 1) staged small-step abstract interpreter (classical AAM),
2) staged big-step abstract interpreter (ADI), 3) staged small-step abstract
interpreter is equivalent to staging a fix-point promoted big-step abstract 
interpreter, 4) soundness after staging.

Question: 1) Pushdown analysis can be obtained if the abstract interpreter is
written in a definitional way. Does pushdown property still exists after 
staging? 2) Pushdown analysis can be complicated in a small-step setting 
\cite{vardoulakis2010cfa2, earl2012introspective, gilray2016pushdown}. 
The Pushdown for Free (P4F for short) \cite{gilray2016pushdown} is probably the most 
simple solution. What is the relation between a staged P4F and a staged 
abstract defintional interpreter?

(ADI in Racket: \url{https://github.com/plum-umd/ abstracting-definitional-interpreters/}).

\section{Improving Performance}

We may show how to generate more efficient code (rather closure).

@@

\section{Modular Analysis for Free?}

@@

Show the evaluation result on benchmark programs.

Compare with normal abstract interpreter, 
abstract compilation\cite{Boucher:1996:ACN:647473.727587}, and OAAM \cite{Johnson:2013:OAA:2500365.2500604}.
Benchmarks and other reference implementations: \url{https://github.com/ilyasergey/reachability}.

\section{Discussion}

@@
